### 2018-07-11 paper/sphinxes.tex
Adds more WIP on Sphinxes

\NewVariable{\sk}{sk}
\NewVariable{\pk}{pk}

@@

\subsubsection{Sphinxes algorithms}

>>>>

\NewVariable{\sk}{x}
\NewVariable{\pk}{X}

@@

\subsubsection{Sphinxes algorithms and \acf*{POR}}

\NewScheme{\Sphinxes}{POR}
\NewAlgorithm{\CreateHeader}{\Sphinxes[CreateHeader]}
\NewAlgorithm{\WrapHeader}{\Sphinxes[WrapHeader]}
\NewAlgorithm{\AttachPayload}{\Sphinxes[AttachPayload]}
\NewAlgorithm{\Process}{\Sphinxes[Process]}

Sphinxes provides the following algorithms:
\begin{itemize}
  \item \(\CreateHeader\) creates a header, this is a modification of that of 
    Sphinx~\cite[\S 3.2, \S 3.4]{Sphinx}.
  \item \(\WrapHeader\) is used to wrap a given single-use reply block given 
    the proper keys.
  \item \(\AttachPayload\) attaches a payload to the header, \ie makes it 
    sendable.
    This is what Sphinx~\cite[\S 3.3]{Sphinx} calls a forward message.
  \item \(\Process\) is the algorithm for processing incoming messages, the 
    processing is identical to Sphinx~\cite[\S 3.6, \S 3.7]{Sphinx} but uses a 
    different interface.
\end{itemize}

\NewVariable{\G}{\mathcal{G}}
\NewVariable{\mac}{\mu}
\NewVariable{\prg}{\rho}
\NewVariable{\prp}{\pi}
\NewVariable{\hash}{h}
%\NewVariable{\tag}{\tau}
\NewVariable{\blind}{b}
\NewVariable{\N}{\mathcal{N}}
\NewVariable{\D}{\mathcal{D}}

We will synchronize our detailed descriptions with that of 
Sphinx~\cite{Sphinx}, hence we will use the following notation:
\begin{itemize}
  \item \(\kappa\) is the security parameter.
    The adversary must thus do about \(2^\kappa\) work to break the security.

  \item \(r\) is the maximum number of nodes (\ie equivalent to the number of 
    layers) that a message will traverse before reaching its destination.

  \item \(\G\) is a prime-order cyclic group satisfying the \ac{DH} assumption.

  \item \(\mac\colon \bin^\kappa\times \bin^*\to \bin^\kappa\) is \iac{MAC}.
    It can be instantiated as \eg SHA256-HMAC-128.

  \item \(\prg\colon \bin^\kappa\to \bin^{(2r+3)\kappa}\) is \iac{PRG}.
    It can be instantiated as any block cipher in counter mode.

  \item \(\prp\colon \bin^\kappa\times \bin^{l_\prp} \to \bin^{l_\prp}\) is 
    \iac{PRP}.
    It can be instantiated using the LIONESS block cipher~\cite{LIONESS}.

  \item \(\hash_\mac, \hash_\prg, \hash_\prp\) are all distinct hash functions 
    of the form \(\bin^\kappa\to \bin^\kappa\).
    They are used as key-derivation functions.

  \item \(\hash_\tau\colon \G^*\to \bin^{2\kappa}\) is used to identify 
    previously seen elements of \(\G^*\).

  \item \(\hash_\blind\colon \G^*\times \G^*\to \ZZ_q^*\) is used to compute 
    blinding factors.
    All the hash functions can be instantiated with truncated versions of hash 
    functions from the SHA-2 and -3 families.

  \item \(\N\subset \bin^\kappa\) is a set of node identifiers.
    Each node \(n\in \N\) has a private key \(\sk_n\in \ZZ_q^*\) and a public 
    key \(\pk_n = g^{\sk_n}\in \G^*\).
    We assume that the identifier--public-key pairs, \((n, \pk_n)\), are 
    distributed.
    (Sphinx made a difference between nodes and destinations, \ie the set 
    \(\D\) such that \(\D\cap \N = \emptyset\) and \(\D\cup \N\) is prefix 
    free, see~\cite{Sphinx} for details.
    We could do the same adoption, but we do not need that for the purposes of 
    this paper.)
    We let \(*\in \N\) be the special identifier of the null node.

  \item \(0_x\) denotes \(x\) zeroes.
    \(s_{[a..b]}\) denotes all bits from the \(a\)th bit to the \(b\)th of the 
    bit string \(s\).
\end{itemize}

\NewAlgorithm{\ComputeKeys}{ComputeKeys}
\NewAlgorithm{\ComputePadding}{ComputePadding}

The \(\CreateHeader\) algorithm is based on that of Sphinx~\cite[\S 
3.2]{Sphinx}.

\Cref{fig:CreateHeader} summarizes the algorithm.

We reveal the maximum number of alternatives per layer.
But we do this in ordinary \ac{OR} too, since there is only one node per layer.

First we generate all the needed keys.

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    \Require{%
      $I\in \bin^\kappa$ is an identifier.
      $L = \{N_0, \dotsc, N_\nu\}$ such that $N_i, N_j\subset \N$, $N_i\cap N_j 
      = \emptyset\}$ for $i\neq j$, and $\nu+1 = |L| \leq r$.
      $N_\nu$ is the destination.
    }
    \Function{\CreateHeader}{$I, L$}
      \State $w_L\gets \max_{N\in L} |N|$
      \Comment{Maximum width of a layer, \ie alternative nodes.}
      \State $w_H\gets (2w_L+2)$
      \Comment{Header width:
        layer nodes' ciphertexts and addresses ($2w_L\kappa$),
        address of next node ($\kappa$),
        \ac{MAC} ($\kappa$).}
      \State $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, C_\nu, 
      b_\nu)\gets \ComputeKeys[L, w_L]$
      \State $\phi_1, \dotsc, \phi_\nu\gets \ComputePadding[\{s_1, \dotsc, 
      s_\nu\}, w_H]$
      \State $\alpha \gets \alpha_\nu$
      \State $C\gets C_\nu$
      \State $\beta \gets
      \left\{\left\{N_\nu\concat
          I\concat
          0_{(2w_L(r-\nu)+2)\kappa}\right\} \oplus
        \prg(\hash_\prg(s_\nu)_{[0..(2w_L(r-\nu)+3)\kappa-1]}\right\}\concat 
      \phi_\nu$
      \Comment{$\beta_\nu$}
      \State $\gamma \gets $
      \Comment{$\gamma_\nu$}
      \For{$\nu-1\leq i\leq 1$}
        \State $(\alpha, C, \beta, \gamma) \gets
          \WrapHeader[i, (\alpha, \beta, \gamma), \alpha_i, s_i, C_i, N_{i+1}, 
          w_L]$
      \EndFor
    \EndFunction

    \Function{\WrapHeader}{$i, (\alpha_{i+1}, \beta_{i+1}, \gamma_{i+1}), 
      \alpha_i, s_i, C_i, N_{i+1}, w_L$}
      \If{$i < 1$}
        \Return $\bot$
      \EndIf
      \State $\beta_i \gets \{N_{i+1}, \concat \gamma_{i+1}\concat 
      (\beta_{i+1})_{[0..(w_L r-1)\kappa -1]}\}$
      \State $\gamma_i \gets \mac(\hash_\mac(s_i), \beta_i)$
      \Return $i-1, (\alpha_i, C_i, \beta_i, \gamma_i)$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:CreateHeader}%
    \dots
  }
\end{figure}

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    \Function{\ComputeKeys}{$L = \{L_1, \dotsc, L_l\}, w_L$}
      \State $\sk\rgets \ZZ_q^*, \pk\gets g^\sk$
      \State $\alpha_0\gets \pk$
      \State $s_0\rgets \bin^\kappa$
      \Comment{Differs from Sphinx.}
      \For{$1\leq i\leq |N_0|$}
        \State $s_0^{(i)}\gets \pk_{n_i}^\sk$, where $n_i\in |N_0|$.
        \State $c_0^{(i)}\gets \Enc[_{s_0^{(i)}}][s_0]$
      \EndFor
      \For{$|N_0|+1\leq i\leq w_L$}
        \State $c_0^{(i)}\rgets \bin^\kappa$
      \EndFor
      \State $C_0\gets (c_0^{(1)}, \dotsc, c_0^{(w)})$
      \State $b_0\gets \hash_\blind(\alpha_0, s_0)$
      \Comment{Same as Sphinx.}
      \For{$1\leq i < \nu$}
        \State Compute $(\alpha_i, C_i, \beta_i, \gamma_i)$ as follows.
        \State $\alpha_i = \pk^{b_{i-1}}$
        \State $s_i\rgets \bin^\kappa$
        \Comment{Differs from Sphinx.}
        \For{$1\leq j\leq |N_i|$}
          \State $s_i^{(j)}\gets \pk_{n_j}^\sk$, where $n_j\in |N_i|$.
          \State $c_i^{(j)}\gets \Enc[_{s_i^{(j)}}][s_i]$
        \EndFor
        \For{$|N_i|+1\leq i\leq w_L$}
          \State $c_0^{(i)}\rgets \bin^\kappa$
        \EndFor
        \State $C_i\gets (c_i^{(1)}, \dotsc, c_i^{(w)})$
        \Comment{Same as Sphinx.}
        \State $b_i\gets \hash_\blind(\alpha_i, s_i)$
      \EndFor
      \State \Return $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, 
      C_\nu, b_\nu)$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:SphinxesKeys}%
    \dots
  }
\end{figure}

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    \Function{\ComputePadding}{$\{s_1, \dotsc, s_\nu\}, w_H$}
      \State $\phi_1\gets \epsilon$
      \Comment{$\epsilon$ is the empty string.}
      \For{$2\leq i\leq \nu$}
        \State $\phi_i = \{ \phi_{i-1}\concat 0_{w_H} \} \oplus
          \{ \prg(\hash_\prg(s_{i-1}))_{[(w_H(r-i+1)+3)\kappa..(w_H 
            r+3)\kappa-1]} \}$
      \EndFor
      \State \Return $\phi_1, \dotsc, \phi_\nu$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{fig:SphinxesPadding}%
    \dots
  }
\end{figure}
